\LARGE \bf Detection of design pattern : A systematic mapping study

### 2016-01-02 article/main.tex
[fix] typo

Disagreement in the rating of article inside a pair were firstly dealt with a
reconsidaration of the rating of each individual according to the arguments of his opposing rater.
In the case of unresolved disagreement, we brought our case before a senior
researcher that published in the studied field who would instruct us over the final
decision.
If even he could settle de disagreement, the article was included to possibly be
excluded at a later point.

>>>>

Disagreement in the rating of article inside a pair were firstly dealt with a
reconsideration of the rating of each individual according to the arguments of his opposing rater.
In the case of unresolved disagreement, we brought our case before a senior
researcher that published in the studied field who would instruct us over the final
decision.
If even he could settle de disagreement, the article was included to possibly be
excluded at a later point.
